Univalent Universes and Completness of Reversible Programs

### 2017-02-09 upi.tex
more on equivalence statement

The univalent universe is $\Sigma_{X:\mathbf{Type}} \| X \equiv \mathbb{2} \|_1$ where \ldots

@@

>>>>

We assume an ambient univalent universe defined like in the HoTT book and including dependent pairs, a unit type, coproducts, identity types, and constants $\textsc{funext}$ and $\textsc{univalence}$. Our universe $\mathcal{U}$ is the subuniverse of this ambient universe defined as $\Sigma_{X:\mathbf{Type}} \| X \equiv \mathbb{2} \|_1$ where:

\begin{itemize}

\item $\Sigma$ is the type former for dependent pairs: it comes equipped with an introduction rule, an induction principle, and a computational rule.

\item $\mathbb{2}$ is the type of booleans which comes with the two points, an induction principle, and computational rules.

\item $\equiv$ is the identity type former which comes with $\reflp$, an induction principle $J$, and a computation rule.

\item $\| A \|_1$ is the 1-truncation of $A$ defined as follows: for all $x,y:A$ and $p,q : x \equiv y$ and $\alpha,\beta : p \equiv q$, we have $\alpha=\beta$.

\end{itemize}

@@

Now we claim that $\mathcal{U}_\Pi$ is equivalent to $\mathcal{U}$ where $\mathcal{U}_\Pi$ is a universe which includes types $\tau$ as a points, combinators $c : \tau_1 \iso \tau_2$ as 1-paths, and 2-combinators $\alpha : c_1 \isotwo c_2$ as 2-paths.
